Hydras and Cie \\ Variations on Kirby \& Paris' hydra battles and ordinal numbers in Coq

### 2021-09-24 doc/JFLA2022/paper.tex
fix a few typos

\begin{theorem}
  n the Hydra game, Hercules eventually wins, whichever the strategy of both players :
  choice of a head to chop off, choice of the number of copies. 
 \label{kp:thm1}
\end{theorem}

>>>>

\begin{theorem}
  In the Hydra game, Hercules eventually wins, whichever the strategy of both players :
  choice of a head to chop off, choice of the number of copies. 
 \label{kp:thm1}
\end{theorem}
